Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-11-15 papers/2012-sandwich/support.tex
edited support file
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2241 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1341.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{Structure with and without electric field, with disclination lines
removed for clarity. Panels A and B reproduce the results Fig. 3 panels
C and D with the applied field in the $x$-direction (into the plane of the
paper). Also included is a cut of the structure factor with $k_y = 0$
(panel C). Panels D, E, and F show the corresponding situation after the
external field has been removed and the structure allowed to relax,
and show residual hexagonal ordering. The structure factor data is for wave
vectors $k_x = 0; (k_y, k_z) \in [-3\pi/8 , 3\pi/8]$ (panels B and E) and
$k_y = 0; (k_x, k_z) \in [-3\pi/8, 3\pi/8]$ (panels C and F).
[ADD PARTICLE Y-VIEW?]}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}\\
\end{center}
\caption{Cycling the electric field. Starting from the final position of
Supplementary Fig.~7 panel~C, the field is re-applied, this time in the
$y$-direction. The corresponding view of the particle distribution is
shown, again viewing along the field direction, in panel A.
Corresponding structure factor cuts with $k_x = 0$ and $k_y = 0$ are
shown in panels B and C, respectively. The corresponding situation when
the field is again switched off, and the structure allowed to relax,
is shown in panels d, E, and F. The wave vector values used are the
same as in Supplementary Fig.~7. [ADD PARTIVLE $y$-VIEW?]}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{Cycling the electric field further. Starting from the final
position of Supplementary Fig.~8 panel~D, the field is re-applied
again in the $x-$direction. Panel A shows the particle configuration
viewed along the field direction, and panels B and C show the structure
factor with $k_x = 0$ and $k_y = 0$ respectively. The corresponding
situation when the field is removed and the structure allowed to relax
is shown in panels D, E, and F. The wave vector values are again as
in Supplementary Fig.~7. [DIFFERENCE CF 7?]}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1341.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{Structure with and without electric field, with disclination lines
removed for clarity. Panels A and B reproduce the results in Fig. 3C and
Fig. 3D respectively with the applied field in the $x$-direction 
(out of the plane of the paper). Also included is a cut of the structure 
factor with $k_y = 0$ (panel C). 
Panels D, E, and F show the corresponding situation after the
external field has been removed and the structure allowed to relax,
and show residual hexagonal ordering. The structure factor data is for wave
vectors $k_x = 0; (k_y, k_z) \in [-3\pi/8 , 3\pi/8]$ (panels B and E) and
$k_y = 0; (k_x, k_z) \in [-3\pi/8, 3\pi/8]$ (panels C and F).}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}\\
\end{center}
\caption{Cycling the electric field. Starting from the final position of
Supplementary Fig.~7 panel~D, the field is re-applied, this time in the
$y$-direction. The corresponding view of the particle distribution is
shown, again viewing along the field direction, in panel A.
Corresponding structure factor cuts with $k_x = 0$ and $k_y = 0$ are
shown in panels B and C, respectively. The corresponding situation when
the field is again switched off, and the structure allowed to relax,
is shown in panels d, E, and F. The wave vector values used are the
same as in Supplementary Fig.~7.}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{Cycling the electric field further. Starting from the final
position of Supplementary Fig.~8 panel~D, the field is re-applied
again in the $x-$direction. Panel A shows the particle configuration
viewed along the field direction, and panels B and C show the structure
factor with $k_x = 0$ and $k_y = 0$ respectively. The corresponding
situation when the field is removed and the structure allowed to relax
is shown in panels D, E, and F. The wave vector values are again as
in Supplementary Fig.~7. Note that the on and off states are 
equivalent to those in Supplementary Fig.~7, up to a rotation.
This is because all hexagonal structures perpendicular to the field
direction are energetically degenerate,
and the actual orientation of the hexagon emerges spontaneously during
switching. }
\end{figure}
